\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-10 article.tex
Added in-text reference

  Combined in a pattern, it allows the student to systematically deal with one
  or several imaginary opponents under various assumptions, using every
  available attacking and blocking tool from different directions. In
  addition, the techniques should also be evenly distributed between the left
  and the right side\cite{cyclo:vol1}.

>>>>

  Combined in a pattern, it allows the student to systematically deal with one
  or several imaginary opponents under various assumptions, using every
  available attacking and blocking tool from different
  directions\cite{cyclo:vol1}. In addition, the techniques should also be
  evenly distributed between the left and the right side\cite{cyclo:vol1}.
